% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{David Hacker\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Contact Information} \\ 
	Email: dmhacker@yahoo.com \\ 
	Website: dmhacker.github.io  \\
        Phone: (805) 368-5071 }
\address{{\bf Present Address} \\ 
	\#60318 9450 Gilman Dr.  \\
        La Jolla, CA 92092-0100 }

\begin{resume} 

\section{Education} 
B.S. in Computer Science \hfill June 2021 \\
University of California, San Diego

\section{Experience}
 {\bf Application Developer,} MyGolfFaves \hfill June 2017 – Sep 2017
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Used React Native to create iOS and Android apps \\
                 for MyGolfFaves, a golfing discounts company.
 \end{itemize}
 
{\bf Full Stack Developer,} Blinks \hfill July 2016 – Jan 2017
\begin{itemize} \itemsep -2pt %reduce space between items
\item  Improved the resource demands and efficiency of \\
		Blink's Android app.
\item  Created a backend to support Blink's iOS sticker \\
		subscription service using the MEAN stack, mLab, \\ 
		Amazon S3 and Cloudfront.
\item  Designed a corresponding admin panel.
\end{itemize}

{\bf Full Stack Developer,} IndieU \hfill Mar 2016 – Aug 2016       
\begin{itemize} \itemsep -2pt
\item  Redesigned the website for IndieU, a music streaming \\ 
		service for college students. 
\item Involved numerous layout changes and required \\ 
		knowledge of the MEAN stack.
\end{itemize}

\section{Projects} 
{\bf Alexa YouTube Skill} \hfill Node.JS, Lambda, Heroku
\begin{itemize} \itemsep -2pt
\item   An unpublished skill that lets Amazon Alexa \\ devices play audio from YouTube videos
\end{itemize}

{\bf Photorealistic Rendering Engine} \hfill Java, Swing
\begin{itemize} \itemsep -2pt
\item  Configurable, multi-threaded ray tracer
\item  Options: Vertex normal interpolation, Phong shading, \\
		ray reflection \& transmission, balanced k-d tree generation, \\
		camera rotation, and anti-aliasing.
\end{itemize}

{\bf Text Compression Experiments} \hfill Python, Numpy
\begin{itemize} \itemsep -2pt
\item  Custom compression algorithm combining existing designs
\item  Uses: Burrows-Wheeler transform, move-to-front transform, \\ 
		run-length encoding, Huffman encoding

\end{itemize}

\section{Honors \& \\ Awards} 
1st Place, Startup Weekend Conejo Valley 2017 \\
Honorable Mention, SIAM M3 Challenge 2017 \\
3rd Place, MIT Zero Robotics 2015 \& 2016 \\
National Merit Finalist \\
Eagle Scout

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & Java, Python, JavaScript, C++, HTML, CSS \\

     \underline{Frameworks:} & MEAN stack, Matplotlib, Numpy, Keras, Firebase, React Native, Materialize, Bootstrap 
 \end{tabular}

\end{resume} 
\end{document} 



