\documentclass[fontsize=11pt]{article}
    \usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage[svgnames]{xcolor}  % Colours by their 'svgnames'
\usepackage[margin=0.75in]{geometry}
  \textheight=700px
\usepackage{url}
\usepackage{lmodern} % Allow arbitrary font sizes
\usepackage{textcomp}

%% Define a new 'modern' style for the url package that will use a smaller font.
\makeatletter
\def\url@modernstyle{
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{}}}
\makeatother
\urlstyle{modern} %% And use the newly defined style.

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

\renewcommand{\familydefault}{\sfdefault}

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}

\sectionfont{                 % Change font of \section command
  \usefont{OT1}{phv}{b}{n}%   % bch-b-n: CharterBT-Bold font
  \sectionrule{0pt}{0pt}{-5pt}{3pt}}

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}      % Box to align text
\newcommand{\sepspace}{\vspace*{1em}}   % Vertical space macro

\newcommand{\MyName}[1]{ % Name
    \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
    \par \normalsize \normalfont}

\newcommand{\MySlogan}[1]{ % Slogan (optional)
    \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
    \par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
    \noindent\hangindent=2em\hangafter=0 % Indentation
    \parbox{\spacebox}{                  % Box to align text
    \textit{#1}}                      % Entry name (birth, address, etc.)
    \hspace{1.5em} #2 \par}              % Entry value

\newcommand{\SkillsEntry}[2]{                % Same as \PersonalEntry
    \noindent\hangindent=2em\hangafter=0 % Indentation
    \parbox{\spacebox}{                  % Box to align text
    \textit{#1}}                    % Entry name (birth, address, etc.)
    \hspace{1.5em} #2 \par}              % Entry value

\newcommand{\AwardsEntry}[2]{                % Same as \PersonalEntry
    \noindent\hangindent=2em\hangafter=0 % Indentation
    \parbox{\spacebox}{                  % Box to align text
    \textit{#1}}                    % Entry name (birth, address, etc.)
    \hspace{1.5em} #2 \par}              % Entry value

\newcommand{\EducationEntry}[4]{
    \noindent \textbf{#1} \hfill      % Study
    \colorbox{Black}{
      \parbox{8.5em}{
      \hfill\color{White}#2}} \par  % Duration
    \noindent \textit{#3} \par        % School
    \noindent\hangindent=2em\hangafter=0 \small #4 % Description
    \normalsize \par}

\newcommand{\WorkEntry}[4]{       % Same as \EducationEntry
    \noindent \textbf{#1} \hfill      % Jobname
    \colorbox{Black}{%
      \parbox{9em}{%
      \hfill\color{White}#2}} \par   % Duration
        \noindent \textit{#3} \par        % Company
    \noindent\hangindent=2em\hangafter=0 \small #4 % Description
    \normalsize \par}

\newcommand{\ProjectEntry}[4]{         % Similar to \EducationEntry
    \noindent \textbf{#1} \noindent \textit{#3} \hfill {#2} \par
    \noindent \small #4 % Description
    \normalsize \par}

\newcommand{\AwardEntry}[4]{         % Similar to \EducationEntry
    \noindent \textbf{#1} \noindent \textit{#3} \hfill {#2} \par
    \noindent \small #4 % Description
    \normalsize \par}
    \begin{document}
\MyName{David Hacker}
\bigskip
{\small \hfill dmhacker@yahoo.com | (805) 368-5071 | Thousand Oaks, CA | github.com/dmhacker}
    
%%% Education
%%% ------------------------------------------------------------
\NewPart{Education}{}
\EducationEntry
{BS Computer Science}
{June 2021}
{University of California, San Diego, La Jolla, CA}
  
%%% Work experience
%%% ------------------------------------------------------------
\NewPart{Work Experience}{}

\WorkEntry
{Software Consultant}
{March 2016 - Present}
{Pinnacle Coding, Westlake Village, CA}
{\begin{itemize} \itemsep -1pt
	\item Redesigned the website for IndieU, a music sharing company. Involved numerous layout changes and required knowledge of the MEAN stack.
	\item Improved the resource demands and efficiency of the Android app for Blinks, a company that used Eddystone beacons to broadcast information about retail stores and their wares.
	\item When Blinks pivoted to being a subscription service for iOS stickers, I designed a functional backend to hold all of their stickers. Used the MEAN stack, mLab, Amazon S3 for image storage, and Cloudfront.
	\item Using React Native, created iOS and Android apps for MyGolfFaves, a golfing rewards/discounts company.
	\end{itemize}}
%%% Skills
%%% ------------------------------------------------------------
\NewPart{Skills}{}
\SkillsEntry{Proficient in}{Java, Python, C++}
\SkillsEntry{Backend}{MEAN stack, Django, Flask, Golang, Firebase}
\SkillsEntry{Frontend}{HTML, CSS, Javascript, Bootstrap, Google Material Design}
%%% Projects
%%% ------------------------------------------------------------
\NewPart{Projects}{}

\ProjectEntry{Photorealistic Rendering: Recursive Ray Tracer}{https://github.com/dmhacker/RenderingEngine}
{Java}
{Configurable options for a variety of features: vertex normal interpolation using barycentric coordinates, Phong shading, ray reflection \& transmission, balanced k-d tree generation, camera rotation, and anti-aliasing}
\sepspace

\ProjectEntry{Text Compression Experiments}{https://github.com/dmhacker/yatc}
{Python}
{Custom compression algorithm combining existing designs: Burrows-Wheeler transform, move-to-front transform, run-length encoding, Huffman encoding}
\sepspace

\ProjectEntry{Alexa YouTube Skill}{https://github.com/dmhacker/alexa-youtube-skill}
{Node.js, JavaScript}
{An unpublished skill that lets Amazon Alexa devices play audio from YouTube videos}
%%% Awards
%%% ------------------------------------------------------------
\NewPart{Awards}{}

\AwardEntry{Honorable Mention: SIAM M3 Challenge}{Westlake Village, CA}
{March 2017}
{I designed a crucial regression algorithm using a Fourier series approximation, helping net our team an honorable mention (awarded to the top 8\% of teams); implemented the algorithm in Python using matplotlib and numpy; and automated data collection/processing for other parts of the challenge}
\sepspace

\AwardEntry{International Finalist: MIT Zero Robotics 2016}{Cambridge, MA}
{January 2017}
{See the 2015 version of this award for more details.}
\sepspace

\AwardEntry{International Finalist: MIT Zero Robotics 2015}{Cambridge, MA}
{January 2016}
{My team went the finals hosted at MIT and ended in 3rd place out of nearly 200 international teams. Additionally, my code was run aboard the International Space Station (ISS). I designed four winning strategies for each phase in C++ and taught and directed other members of the team.}
\ 
\end{document}